Measuring Perceptions and Preferences for Meritocracy

### 2021-07-02 paper_study1.Rmd
update plot
- footnote source label

p4<-likert_issp %>% 
  dplyr::select(family_r:child_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference Non-meritocratic",
                        geom.size = c(0.6*size),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = F,
                        reverse.scale = F,
                        show.n = FALSE) +
  ggplot2::labs(caption = paste0("n=",dim(likert_issp)[1]))+
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_brewer(breaks=c(5:1),
                             direction = -1,
                             labels = c("Not important at all","Not very important",
                                        "Fairly important","Very important","Essential"))
```

```{r likert-issp,fig.height=10,fig.width=12,fig.cap="Distribution of responses in the ISSP meritocracy items"}
# plot_likert_issp
cowplot::plot_grid(p1,p2,p3,p4,
                     align = "hv", 
                     axis = "a",
                     nrow = 4, 
                     ncol = 1,
                     rel_heights = c(1,2,1,1.3))
```

>>>>

p4<-likert_issp %>% 
  dplyr::select(family_r:child_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference Non-meritocratic",
                        geom.size = c(0.6*size),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = F,
                        reverse.scale = F,
                        show.n = FALSE) +
  ggplot2::labs(caption = paste0("Source: Authors calculation based on International Social Survey Programme - Social Inequality 2009"," (n=",dim(likert_issp)[1],")"))+
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::scale_fill_brewer(breaks=c(5:1),
                             direction = -1,
                             labels = c("Not important at all","Not very important",
                                        "Fairly important","Very important","Essential"))
```

```{r likert-issp,fig.height=10,fig.width=12,fig.cap="Distribution of responses in the ISSP meritocracy items"}
# plot_likert_issp
cowplot::plot_grid(p1,p2,p3,p4,
                     align = "hv", 
                     axis = "a",
                     nrow = 4, 
                     ncol = 1,
                     rel_heights = c(1,
                                     2.1,
                                     1,
                                     1.3))
```
